Incentivizing Exploration by Heterogeneous Users

### 2018-06-06 Discussion-Proof.tex
typo

\begin{rtheorem}{Theorem}{\ref{rst:known-p}}
Under Assumption~\ref{a:known-p}, the Known-\MinProb Algorithm has an expected payment bounded above by 
$\pfedit{O\left(N^2 \max\{1, (L/p)^{5/2}\}\right)}$.
and an expected regret bounded above by
\bcedit{
\begin{align*}
O\left(\frac{\ARMNUM^2}{\MinProb^2}
    + \frac{\ARMNUM^2}{\hat{z}^2} + \frac{\ARMNUM}{\hat{z}^3}
    + \frac{NL\log^3(T)}{p}    
    \right)
\end{align*}
}
\end{rtheorem}

>>>>

\begin{rtheorem}{Theorem}{\ref{rst:known-p}}
Under Assumption~\ref{a:known-p}, the Known-\MinProb Algorithm has an expected payment bounded above by 
$\pfedit{O\left(N^2 \max\{1, (L/p)^{5/2}\}\right)}$
and an expected regret bounded above by
\bcedit{
\begin{align*}
O\left(\frac{\ARMNUM^2}{\MinProb^2}
    + \frac{\ARMNUM^2}{\hat{z}^2} + \frac{\ARMNUM}{\hat{z}^3}
    + \frac{NL\log^3(T)}{p}    
    \right)
\end{align*}
}
\end{rtheorem}
